Exploring Design Space for Differentially Private Bayesian Inference

### 2019-01-04 ICML2019/main.tex
update abstract

\begin{abstract} Bayesian inference is a statistical method which
allows to derive a \emph{posterior} distribution,
starting from a \emph{prior} distribution and observed data. Several
approaches have been explored in order to make this process differentially
private. For example \cite{dimitrakakis2014robust} and
\cite{wang2015privacy} proved the differentially privacy ofsampling from
the posterior distribution under specific conditions, \cite{zhang2016differential} and \cite{foulds2016theory}
designed differentially private mechanisms that output a
representation of the full posterior distribution. 
% When the output of a differentially private mechanism is a probability
% distribution, accuracy is naturally measured by means of
% \emph{probabilistic distances} measuring how far this distribution is
% from the original one. Some classical examples are total variation distance,
% Hellinger distance, $\chi^2$-distance, KL-divergence, etc.
Laplace mechanism is mostly used while exponential mechanisms have not yet been fully explored. Also, $\ell_1$ norm is mainly used to measure the accuracy while \emph{probabilistic distances} are more suitable when the output of a differentially private mechanism is a probability distribution.

In this work, we explore the design space for differentially private bayesian inference mechanism, by considering different metrics and different algorithms. 
We focused on two discrete models, the Beta-Binomial and the
Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
We explore three main mechanisms based on the Laplace algorithm family and exponential algorithm family. Also, we apply different metric them by calibrating noise to the sensitivity of that utility function, where the utility function is the probability metric we want to
use to measure accuracy. To show the usefulness of these mechanisms we
show an experimental analysis comparing their performance.
\end{abstract}
 % TODO: replace with your keywords

>>>>

\begin{abstract} Bayesian inference is a statistical method which
allows to derive a \emph{posterior} distribution,
starting from a \emph{prior} distribution and observed data. Several
approaches have been explored in order to make this process differentially
private. For example \cite{dimitrakakis2014robust} and
\cite{wang2015privacy} proved the differential privacy of sampling from
the posterior distribution under specific conditions, \cite{zhang2016differential} and \cite{foulds2016theory}
designed differentially private (DP) mechanisms for this inference process. 
% When the output of a differentially private mechanism is a probability
% distribution, accuracy is naturally measured by means of
% \emph{probabilistic distances} measuring how far this distribution is
% from the original one. Some classical examples are total variation distance,
% Hellinger distance, $\chi^2$-distance, KL-divergence, etc.
Laplace mechanism is mostly used while exponential mechanisms have not yet been fully explored. Also, $\ell_1$ norm is mainly used to measure the accuracy while \emph{probabilistic distances} are more suitable when the output of a DP mechanism is a probability distribution.

In this work, we explore the design space for DP bayesian inference, by considering different metrics and different algorithms. 
We focused on two discrete models, the Beta-Binomial and the
Dirichlet-multinomial models, and one distribution distance, Hellinger distance. 
We design mechanisms based on the Laplace algorithm and exponential algorithm and adopt different metrics in them by calibrating noise to the sensitivity of metric that we want to
use to measure accuracy. To show the usefulness of these mechanisms we
show experimental analysis on their performance.
\end{abstract}
 % TODO: replace with your keywords
